Writing a reproducible paper with RStudio and Quarto

### 2023-04-07 paper.qmd
Small correction

5. Finally store these four files together in one folder (and use this folder as your working directory later on), close any open Rstudio instances and directly open `paper.qmd` with a new Rstudio instance. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files. Then click on "Render".[^1]

>>>>

5. Finally store these files together in one folder (and use this folder as your working directory later on), close any open Rstudio instances and directly open `paper.qmd` with a new Rstudio instance. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files. Then click on "Render".[^1]
